---
title: "Making a presentation in R"
author: "Lavinia Gordon"
date: "3 May 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This page 

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Changing fonts

Resources!

[Google Fonts](https://fonts.google.com/) provide over 900 free fonts which you can download.
It is very simple to embed your font of choice into your document.

NOTE - fonts with two names, e.g. [Metal Mania](https://fonts.google.com/specimen/Metal+Mania), are linked to with a "+", i.e. "Metal+Mania", but are referred to in the CSS with a space, i.e. "Metal Mania"

# including tweets

Your YAML should include this line under _nature_:  
`beforeInit: "https://platform.twitter.com/widgets.js"`


# including images

I didn't find the general image very helpful so here are some additional notes.
Use include_graphics from knitr.

```{r}
# All defaults
include_graphics(img1_path)
```

```{r, fig.width = 2}
# Small fig.width
include_graphics(img1_path)
```

```{r, fig.width = 4}
# Bigger fig.width
include_graphics(img1_path)
```

```{r  out.width = "20%"}
include_graphics(img1_path) 
```
